Deep Reinforcement Learning for Conservation Decisions

### 2021-06-10 manuscript/manuscript.Rmd
Putting a footnote in the body

The agent interacts with the environment in an iterative loop, whereby the agent only has access to the observation space, action space and the discounted reward signal, $\gamma^t \, r(s_t, a_t)$.
As the agent interacts with the environment by selecting actions according to its policy, $\pi(a_t | o_t)$, the agent will create a trajectory given as $\tau = (s_0, o_0, a_0, \dots, s_{H-1}, o_{H-1}, a_{H-1}, s_H)$^[While there are RL methods for infinite horizon problems, i.e. when $H=\infty$, we will only present methods for episodic or finite horizon POMDPs.].
From these definitions, we can provide an agent's trajectory distribution for a given policy as,

@@

>>>>

The agent interacts with the environment in an iterative loop, whereby the agent only has access to the observation space, action space and the discounted reward signal, $\gamma^t \, r(s_t, a_t)$.
As the agent interacts with the environment by selecting actions according to its policy, $\pi(a_t | o_t)$, the agent will create a trajectory given as $\tau = (s_0, o_0, a_0, \dots, s_{H-1}, o_{H-1}, a_{H-1}, s_H)$.
From these definitions, we can provide an agent's trajectory distribution for a given policy as,

@@

While there are RL methods for infinite horizon problems, i.e. when $H=\infty$, we will only handle episodic or finite horizon POMDPs.
